Pteropod exposure analysis

### 2018-03-12 expose.Rmd
push survivor cor to server

# ranout <- reactive(lme(alive)

@@

```{r}
selectInput("lns", "Choose a variable for line thickness:", envchr)

allv <- allv %>% 
  left_join(envdat, by = 'CTD')

plo <- reactive({

  names(allv)[names(allv) %in% input$lns] <- 'thick'

  p <- ggplot(toplo, aes(x = pco2_trt, colour = temp_trt)) + 
    geom_line(data = allv, aes(y = alive, group = uni, size = thick), alpha = 0.6) +
    geom_point(size = 5, aes(y = ave)) + 
    geom_errorbar(aes(ymin = lov, ymax = hiv), width = 0.1, size = 1.5) +
    geom_line(aes(y = ave, group = temp_trt), size = 1.5) +
    scale_y_continuous('% alive') + 
    theme_bw(base_family = 'serif') + 
    scale_size(input$lns, range = c(0.2, 1.5))

renderPlot({plo()}, height = 300, width = 600)

```

```{r}

selectInput("var", "Choose an environmental variable to model:", envchr)

# full
md <- reactive({

  frm <- formula(paste('asin(alive / 100) ~ (temp_trt + pco2_trt) * ', input$var))
  md <- lm(frm, data = allv)

  return(md)

# with select
md_sel <- reactive({

  frm <- formula(paste('asin(alive / 100) ~ (temp_trt + pco2_trt) * ', input$var))
  md_sel <- lm(frm, data = allv) %>% step(trace = 0)

  return(md_sel)

```

Full model:
```{r}
renderPrint({summary(md())})
```

Final selected model:
```{r}
renderPrint({summary(md_sel())})
```

>>>>

@@

```{r}
# all correlations
crs <- crossing(var1 = 'alive', var2 = envchr) %>% 
  rownames_to_column() %>% 
  group_by(rowname) %>% 
  nest %>% 
  mutate(

    crs = map(data, function(x){

      # variables
      vr1 <- toplo3[[x$var1]]
      vr2 <- toplo3[[x$var2]]

      # pearson
      pr_ts <- cor.test(vr1, vr2, method = 'pearson')
      pr_cr <- round(pr_ts$estimate, 2)
      pr_pv <- p_ast(pr_ts$p.value)
      pr <- paste(pr_cr, pr_pv)

      # spearman
      sp_ts <- suppressWarnings(cor.test(vr1, vr2, method = 'spearman'))
      sp_cr <- round(sp_ts$estimate, 2)
      sp_pv <- p_ast(sp_ts$p.value)
      sp <- paste(sp_cr, sp_pv)

      out <- data.frame(pr = pr, sp = sp, stringsAsFactors = F)
      return(out)

    })
  ) %>% 
  unnest %>% 
  select(-rowname) %>% 
  gather('cortyp', 'corval', pr, sp) %>% 
  spread(var2, corval)
```

```{r}
knitr::kable(crs, caption = 'Pearson and Spearman correlations, based on averages by site')
```
